Main Analyses

### 2016-03-01 Rmd/figures.Rmd
Submitted version 29/2/2016

# Plot
i1 <- rbind(mzto$impacts, soyto$impacts)
crops <- c("maize", "soy", "maize/soy")
# plot(1:10, pch = 20, cex = 4, col = "gold2")
# plot(mzsoyr, col = c("grey", "goldenrod", "green4", "orange"))
imp_plot2(mzsoyr, i1, p_figures, "ideal_yield2", "", crops, 1.2, TRUE, 
         c("red", "blue1", "gold"))

@@

### Figure 1
```{r, eval = FALSE}
load(fp(p_out, "mainresults2502.rda"))

@@

# select out corresponding impact statistics, summarize
conv_stats <- selected_impacts(pure, fp(p_out, ybdc$both$bcode))
# impsr <- lapply(c(2, 5, 3, 7:9, 4), function(x) conv_stats[[x]])
impsr <- lapply(c(2, 3, 8, 5), function(x) conv_stats[[x]])

@@

# plot(1:10, ylab = ylabs[2])
# ylabs <- c("Jaccard Index", 
ylabs <- c(expression(paste("Converted area (", 10^5, " ", km^2, ")")), 
           "Carbon loss (Mt)", #"Priority", 
           "Biodiversity Index", "Travel time (hours)")#,
           # "Intactness", expression(paste("FR converted (ha"^2, ")")))
# yscale <- c(1, 10^5, 1, 100000, 1, 1, 1, 1)
yscale <- c(10^5, 100000, 1, 1)#, 1, 1, 1)
# ftits <- list("Y 100%", "C 100%", "Biod 100%", "Cost 100%")
ftits <- list("Maximize Yields", "Minimize Carbon Loss", 
              "Minimize Biodiversity Loss", "Minimize Travel Time")
# leg <- c("Converted")

yaxes <- list(seq(0, 16, 2), seq(0, 1200, 100), seq(0, 0.6, 0.1), 
              seq(0, 7, 1))#,               
              # seq(0, 1200, 100), #seq(0, 0.12, 0.02)), 
              #seq(0, 1, 0.1), seq(0, 6500, 500))
# bcols <- c(list(c(cols_tr[1], cols_tr[2], cols_tr[1], cols_tr[2], 
#                   cols_tr[3])), lapply(1:7, function(x) rep("black", 4)))

# plot
# tiff(fp(p_figures, "single_priorities2.tif"), height = 3.5, width = 7, 
png(fp(p_figures, "single_priorities2.png"), height = 3.5, width = 7, 
    units = "in", res = 300)
# postscript(fp(p_figures, "single_priorities2.eps"), horizontal = FALSE, 
#            height = 3.5, width = 7)
l <- layout(mat = lmat)
# layout.show(l)

# map plots
legtf <- c(FALSE, FALSE, FALSE, FALSE)
for(i in 1:4) { # i <- 1
  # par(mar = rep(0, 4))
  # plot(zambia, col = cols_tr[i])
  imp_plot2(rs2[[i]], impacts = i1, fpath = p_figures, fnm = "bob",
            crops = "", ftitle = ftits[[i]], col = cols_tr[[i]], 
            legend = legtf[i], hold = TRUE, stats = FALSE, cexscale = 0.4, 
            marg = rep(0, 4))
}  
# impact plots
# mgp <- c(1.6, 0.25, 0)
# par(mar = c(4, 3, 0, 0))
# with(pms2b, {
#   plot(NND, JS, col = cols_tr[c(2, 3, 3, 4, 4, 4)], pch = 16, cex = 1.5, 
#        axes = FALSE, xlab = "", ylab = "", ylim = c(0, 0.3))
#   points(NND, JS, col = cols_tr[c(1, 1, 2, 1, 2, 3)], pch = 20, cex = 1)
#   axis(1, at = seq(0, 230, 20), cex.axis = 0.6, las = 2, mgp = mgp, 
#        tcl = -0.2)
#   axis(2, at = seq(0, 0.3, 0.05), cex.axis = 0.6, las = 2, mgp = mgp, 
#        tcl = -0.2)
#   mtext(text = "NN Distance (km)", side = 1, line = 1, cex = 0.45)
#   mtext(text = "Jaccard Index", side = 2, line = 1.25, cex = 0.45)
# })
mgp <- c(1, 0.25, 0)
# for(i in 1:7) {
cx <- 0.6
for(i in 1:4) {
  v <- impsr[[i]] / yscale[i]
  par(mar = c(2, 3.5, 2, 0))
  b <- barplot(impsr[[i]] / yscale[i], las = 2, col = cols_tr, 
               mgp = c(1, 0.25, 0), tcl = -0.2, yaxt = "n", 
               ylim = range(yaxes[[i]]), ylab = ylabs[i], cex.axis = cx,
               cex.lab = 0.7)
  axis(2, at = yaxes[[i]], cex.axis = cx, las = 2, mgp = mgp, tcl = -0.2)
  # mtext("Impacts", side = 3, cex = 1)
  ind <- which(pms2b[, paste0("Var", i)] == 1)
  with(pms2b[ind, ], {
    par(mar = c(0.5, 3, 2, 1), mgp = mgp)
    barplot(JS, col = cols_tr[-i], ylim = c(0, 30), yaxt = "n", 
            ylab = "% Overlap", cex.lab = cx)
    axis(2, at=seq(0, 30, 10), cex.axis = cx, las = 2, mgp = mgp, tcl = -0.2)
    # mtext("Promixity", side = 3, cex = 1)
    par(mar = c(2, 3, 0.5, 1), mgp = mgp)
    barplot(NND, col = cols_tr[-i], ylim = c(0, 250), las = 2, yaxt = "n", 
            ylab = "", cex.lab = cx)
    axis(2, at=seq(0, 250, 50), cex.axis = cx, las = 2, mgp = mgp, tcl = -0.2)
    mtext("Average distance", side = 2, line = 1.72, cex = 0.4)
    mtext("to neighbor (km)", side = 2, line = 1.2, cex = 0.4)
  })
}
par(xpd = NA)
legx <- grconvertX(0.4, from = "ndc", to = "user")
legy <- grconvertY(0.5, from = "ndc", to = "user")
legend(x = legx, y = legy, legend = "Protected Areas", pch = 15, col = "grey75", 
       bty = "n", pt.cex = 3 * 0.6, cex = 1.5 * 0.6)
dev.off()

@@

### Figures 2 & 3 (probably supplemental)
```{r, eval = FALSE}
# individual maps
png(full_path(p_figures, "all-4-maps.png"), height = 7, width = 7, 
     units = "in", res = 300)
par(mfrow = c(2, 2))#, oma = c(0, 0, 0, 2))
ftitles <- c("Yield", "Carbon", "Biodiversity", "Cost")
legp <- c(TRUE, rep(FALSE, 3))
for(i in 1:4) {
  dtr <- calc(pure_r[[i]][[1:2]] * c(1, 2), sum)
  imp_plot2(dtr, impacts = i1, fpath = p_figures, fnm = "all-4-maps", 
            cexscale = 0.6, ftitle = ftitles[i], crops = c("maize", "soy"), 
            stats = FALSE, hold = TRUE, legend = legp[i], marg = c(0, 0, 2, 0))
}
dev.off()

@@

# select out impacts corresponding to those runs
cstats <- selected_impacts(pind, fp(p_out, ybdc$both$bcode))
cstats <- cstats[, .(iter, conv_area, tot_C, mu_cost, int_prior)]

@@

((minmaxstats[2, c(2:3, 8, 5), with = FALSE]) - 
  (imp_pct[4, c(4:5, 7, 6), with = FALSE])) /
  imp_range[, c(2:3, 8, 5), with = FALSE]

cols_tr <- c(rgb(1, 0, 0), rgb(0, 0, 1), rgb(0, 0.75, 1), rgb(1, 0.75, 0))
# sctab <- do.call(rbind, scens) * 100
cx <- 0.7
# lcols <- c("black", "red", "blue")
# imp_pct[, {
#   png(fp(p_figures, "weight_impact.png"), height = 4, width = 4, 
#       units = "in", res = 300)
#   par(mgp = c(2, 0.75, 0), mar = c(3, 3, 1, 1))
#   plot(conv_area, tot_C, type = "l", xlab = "", ylab = "", #xaxt = "n", 
#   lines(conv_area, int_prior, col = "red")
#   lines(conv_area, mu_cost, col = "blue")
#   axis(1, at = seq(2, 12, 1), cex = cx, cex.axis = cx, line = -0.25, 
#        tcl = -0.2, mgp = c(1, 0.25, 0))
#   axis(2, at = seq(0, 60, 5), las = 2, cex = cx, cex.axis = cx, line = -0.25, 
#        tcl = -0.15, mgp = c(1, 0.25, 0))
#   mtext("% land savings", side = 1, line = 1, cex = cx)
#   mtext("% Carbon/Biodiv/Cost savings", side = 2, line = 1, cex = cx)
#   inms <- c("tot_C", "int_prior", "mu_cost")
#   for(i in 1:length(inms)) {
#     text(conv_area[-1], get(inms[i])[-1], labels = sctab[-1, i + 1], 
#          cex = cx * 0.8, pos = 3, offset = 0.2, col = lcols[i])
#     text(conv_area[1] + 0.1, i, labels = 0, cex = cx * 0.8, pos = 3, 
#          offset = i * 0.15 - 0.2, col = lcols[i])
#   }
#   legend("bottomleft", legend = c("Carbon", "Biodiv", "Cost"), cex = cx,
#          text.col = lcols, col = lcols, bty = "n", lty = 1)
imp_pct[, {
  png(fp(p_figures, "weight_impact4.png"), height = 4, width = 4, 
      units = "in", res = 300)
  plot(xwgts, conv_areap, type = "l", xlab = "", ylab = "", axes = FALSE, 
       ylim = c(0, 55), col = cols_tr[1])
  lines(xwgts, tot_Cp, col = cols_tr[2])
  lines(xwgts, int_priorp, col = cols_tr[3])
  lines(xwgts, mu_costp, col = cols_tr[4])
  axis(1, at = xwgts, labels = seq(0, 90, 10), cex = cx, cex.axis = cx, 
       line = -0.25, tcl = -0.2, mgp = c(1, 0.25, 0))
  axis(2, at = seq(0, 55, 5), las = 2, cex = cx, cex.axis = cx, line = -0.25, 
       tcl = -0.15, mgp = c(1, 0.25, 0))
  mtext("% Weight taken from Yield and divided", side = 1, line = 1, cex = cx)
  mtext("equally between Carbon & Biodiversity", side = 1, line = 1.75, 
        cex = cx)
  mtext("% Avoided Cost", side = 2, line = 1, cex = cx)
  legend("bottomright", 
         legend = c("Yield", "Carbon", "Biodiversity", "Travel time"), 
         cex = cx, text.col = cols_tr, col = cols_tr, bty = "n", lty = 1, 
         inset = c(0, 0.25, 0, 0))
  dev.off()
}]

@@

# indices of costs in other three variables
cost2 <- seq(1, 5, 0.05)
y_comp <- compromise(pare, optirange, cvar = "Y", cost1 = 1.05, cost2 = cost2)
c_comp <- compromise(pare, optirange, cvar = "C", cost1 = 1.05, cost2 = cost2)
bd_comp <- compromise(pare, optirange, cvar = "BD", cost1 = 1.05, cost2 = cost2)
ct_comp <- compromise(pare, optirange, cvar = "COST", cost1 = 1.05, cost2=cost2)
# pare[ind == y_comp["ind"], .(Y, C, BD, COST)] / optirange[1, ]
# pare[ind == c_comp["ind"], .(Y, C, BD, COST)] / optirange[1, ]
# pare[ind == bd_comp["ind"], .(Y, C, BD, COST)] / optirange[1, ]
# pare[ind == ct_comp["ind"], .(Y, C, BD, COST)] / optirange[1, ]

@@

# pull out the impact tables (brief check shows they are the same values)
all_stats <- selected_impacts(unname(pind), fp(p_out, ybdc$both$bcode))
# impsr <- lapply(c(2, 5, 3, 7:9, 4), function(x) all_stats[[x]])
impsr <- lapply(c(2, 3, 8, 5), function(x) all_stats[[x]])

@@

maxes <- sapply(c(2:3, 8, 5), function(j) minmaxstats[[j]][2])
mins <- sapply(c(2:3, 8, 5), function(j) minmaxstats[[j]][1])
ymaxes <- maxes / yscale
ymins <- mins / yscale
pctlines <- rbind(ymins, 
                  t(sapply(c(0.25, 0.5, 0.75), function(x) {
                    (ymaxes - ymins) * x + ymins
                  })), ymaxes)

@@

ftits <- list("Compromise 5% on Yield", "Compromise 5% on Carbon", 
              "Compromise 5% on Biodiversity", "Compromise 5% on Travel Time")
yaxes <- list(seq(0, 16, 4), seq(0, 1200, 100), seq(0, 0.6, 0.1), 
              seq(0, 7, 1))
pcttxt <- c("best", "50%", "worst")

# plot
png(fp(p_figures, "compromise_5pct2.png"), height = 3.5, 
    width = 7, units = "in", res = 300)
l <- layout(mat = lmat)
# layout.show(l)

# map plots
legtf <- c(FALSE, FALSE, FALSE, FALSE)
for(i in 1:4) { # i <- 1
  # plot(zambia)
  imp_plot2(toresr[[i]], impacts = i1, fpath = p_figures, fnm = "bob",
            crops = "", ftitle = ftits[[i]], col = cols_tr[[i]], 
            legend = legtf[i], hold = TRUE, stats = FALSE, cexscale = 0.4, 
            marg = rep(0, 4))
}  
# impact plots
mgp <- c(0.8, 0.25, 0)
cx <- 0.6
for(i in 1:4) { 
  v <- impsr[[i]][1:4] / yscale[i]
  par(mar = c(2, 3.5, 2, 0))
  b <- barplot(v, las = 2, col = cols_tr, mgp = c(1, 0.25, 0), tcl = -0.2, 
               yaxt = "n", ylim = range(yaxes[[i]]), ylab = ylabs[i], 
               cex.axis = cx, cex.lab = 0.7)
  for(j in 1:3) {
    lines(c(-1, 7), rep(pctlines[j + (j - 1), i], 2), lwd = 1, col = "grey50")
    text(4.5, y = rep(pctlines[j + (j - 1), i], 2), labels = pcttxt[j], 
         col = "grey50", xpd = NA, pos = 4, cex = cx * 0.9)
  }
  axis(2, at = yaxes[[i]], cex.axis = cx, las = 2, mgp = mgp, tcl = -0.2)
  ind <- which(pms2bb[, paste0("Var", i)] == 1)
  with(pms2bb[ind, ], {
    par(mar = c(0.5, 3, 2, 1), mgp = mgp)
    barplot(JS, col = cols_tr[-i], ylim = c(0, 70), yaxt = "n", 
            ylab = "% Overlap", cex.lab = cx)
    axis(2, at=seq(0, 70, 10), cex.axis = cx, las = 2, mgp = mgp, tcl = -0.2)
    par(mar = c(2, 3, 0.5, 1), mgp = mgp)
    barplot(NND, col = cols_tr[-i], ylim = c(0, 30), las = 2, yaxt = "n", 
            ylab = "", cex.lab = cx)
    axis(2, at=seq(0, 30, 10), cex.axis = cx, las = 2, mgp = mgp, tcl = -0.2)
    mtext("Average distance", side = 2, line = 1.3, cex = 0.4)
    mtext("to neighbor (km)", side = 2, line = 0.8, cex = 0.4)
  })
}
par(xpd = NA)
legx <- grconvertX(0.4, from = "ndc", to = "user")
legy <- grconvertY(0.5, from = "ndc", to = "user")
legend(x = legx, y = legy, legend = "Protected Areas", pch = 15, col = "grey75",        bty = "n", pt.cex = 3 * 0.6, cex = 1.5 * 0.6)
dev.off()

@@

png(fp(p_figures, "compromise_25pct.png"), height = 2, width = 4, 
    units = "in", res = 300)
l <- layout(mat = lmat)
# layout.show(l)

@@

for(i in 1:4) {
  1 - print(all_stats[5, c(2:3, 8, 5), with = FALSE] / 
              all_stats[i, c(2:3, 8, 5), with = FALSE])
}

for(i in 1:5) {
  print(((minmaxstats[2, c(2:3, 8, 5), with = FALSE]) - 
     (all_stats[i, c(2:3, 8, 5), with = FALSE])) /
    imp_range[, c(2:3, 8, 5), with = FALSE])
}

@@

ftits <- c("Maximize Yields", "Compromise Equally")
leg <- c("converted", "farmblock", "converted in farmblock")
inlist <- list("Y" = yfbr, "eqwt" = eqfbr)
png(fp(p_figures, "fb_overlaps.png"), height = 2.5, width = 5, units = "in", 
     res = 300)
par(mfrow = c(1, 2))
for(i in 1:2) {
  imp_plot2(inlist[[i]], impacts = i1, fpath = p_figures, fnm = "bob",
            crops = leg, ftitle = ftits[i], 
            col = c("red", "orange", rgb(0, 1, 1)),
            legend = TRUE, hold = TRUE, stats = FALSE, cexscale = 0.3, 
            marg = c(0, 0, 1, 0), inset = c(0, 0, 0, 0), titline = 0)
  mtext(paste("Jaccard Index =", round(fb_sim[i], 2)), side = 3, line = -2, 
        cex = 0.4, adj = 0.2)
  mtext(paste("NN Distance =", round(fb_nnd[i]), "km"), side = 3, line = -2.5, 
        cex = 0.4, adj = 0.2)
}
dev.off()

@@

lowi <- selected_impacts2(lowgap$impacts)
highi <- selected_impacts2(highgap$impacts)
gaptab <- rbind(lowi, all_stats[5, names(all_stats)[-1], with = FALSE], highi)
gaptab[1, ] / gaptab[2, ]
gaptab[, tot_C / 100000]

@@

### Additional supplementals
```{r, eval = FALSE}
il <- mzsoyto$inputs
ylds <- dt_to_raster(cbind(basedt[, .(x, y)], il$p_yield), CRSobj)
carb <- dt_to_raster(cbind(basedt[, .(x, y)], il$carbon), CRSobj)
cost <- dt_to_raster(cbind(basedt[, .(x, y)], il$cost), CRSobj)
closs <- carb[[1]] + carb[[2]] * 0.25
pacols <- c("transparent", "grey85", "grey75")

>>>>

# Plot
i1 <- rbind(mzto$impacts, soyto$impacts)
crops <- c("maize", "soy", "maize/soy")
# plot(1:10, pch = 20, cex = 4, col = "gold2")
# plot(mzsoyr, col = c("grey", "goldenrod", "green4", "orange"))
imp_plot2(mzsoyr, i1, p_figures, "ideal_yield3", "", crops, 1.2, TRUE, 
         c("red", "blue1", "gold"))

@@

### Figure 1
```{r, eval = FALSE}
load(fp(p_out, "mainresults2802.rda"))

@@

# select out corresponding impact statistics, summarize
conv_stats <- selected_impacts(pure, fp(p_out, ybdc$both$bcode)) 
# selected_impacts(pure, fp(p_out, ybdc$both$bcode)) / 100000
conv_stats[1, ] / conv_stats[3, ]

# impsr <- lapply(c(2, 5, 3, 7:9, 4), function(x) conv_stats[[x]])
impsr <- lapply(c(2, 3, 5, 4), function(x) conv_stats[[x]])
# impacts[ind %in% pure]

@@

ylabs <- c(expression(paste("Converted area (", km^2, " X ", 10^-5, ")")), 
           "Carbon loss (Mt)", #"Priority", 
           expression(paste("Biodiversity Index X ", 10^-5)),
           expression(paste("Truck hours X ", 10^-5)))#,
           # "Intactness", expression(paste("FR converted (ha"^2, ")")))
# yscale <- c(1, 10^5, 1, 100000, 1, 1, 1, 1)
yscale <- rep(100000, 4)#, 10000, 10000)#, 1, 1, 1)
ftits <- list("Maximize Yields", "Minimize Carbon Loss", 
              "Minimize Biodiversity Loss", "Minimize Travel Cost")
# leg <- c("Converted")
yaxes <- list(seq(0, 16, 2), seq(0, 1200, 100), seq(0, 9, 1), 
              seq(0, 35, 5))#,               
              # seq(0, 1200, 100), #seq(0, 0.12, 0.02)), 
              #seq(0, 1, 0.1), seq(0, 6500, 500))
# bcols <- c(list(c(cols_tr[1], cols_tr[2], cols_tr[1], cols_tr[2], 
#                   cols_tr[3])), lapply(1:7, function(x) rep("black", 4)))

# plot
# tiff(fp(p_figures, "single_priorities2.tif"), height = 3.5, width = 7, 
png(fp(p_figures, "single_priorities3.png"), height = 3.5, width = 7, 
    units = "in", res = 300)
# postscript(fp(p_figures, "single_priorities2.eps"), horizontal = FALSE, 
#            height = 3.5, width = 7)
l <- layout(mat = lmat)
# layout.show(l)

# map plots
legtf <- c(FALSE, FALSE, FALSE, FALSE)
for(i in 1:4) { # i <- 1
  # par(mar = rep(0, 4))
  # plot(zambia, col = cols_tr[i])
  imp_plot2(rs2[[i]], impacts = i1, fpath = p_figures, fnm = "bob",
            crops = "", ftitle = ftits[[i]], col = cols_tr[[i]], 
            legend = legtf[i], hold = TRUE, stats = FALSE, cexscale = 0.4, 
            marg = rep(0, 4))
}  
# overlap/NND impact plots (recover from commit before 28/2 if needed)
mgp <- c(1, 0.25, 0)
# for(i in 1:7) {
cx <- 0.6
for(i in 1:4) { # i <- 3
  v <- impsr[[i]] / yscale[i]
  par(mar = c(2, 3.5, 2, 0))
  b <- barplot(impsr[[i]] / yscale[i], las = 2, col = cols_tr, 
               mgp = c(1, 0.25, 0), tcl = -0.2, yaxt = "n", 
               ylim = range(yaxes[[i]]), ylab = ylabs[i], cex.axis = cx,
               cex.lab = 0.7)
  axis(2, at = yaxes[[i]], cex.axis = cx, las = 2, mgp = mgp, tcl = -0.2)
  # mtext("Impacts", side = 3, cex = 1)
  ind <- which(pms2b[, paste0("Var", i)] == 1)
  with(pms2b[ind, ], {
    par(mar = c(0.5, 3, 2, 1), mgp = mgp)
    barplot(JS, col = cols_tr[-i], ylim = c(0, 30), yaxt = "n", 
            ylab = "% Overlap", cex.lab = cx)
    axis(2, at=seq(0, 30, 10), cex.axis = cx, las = 2, mgp = mgp, tcl = -0.2)
    # mtext("Promixity", side = 3, cex = 1)
    par(mar = c(2, 3, 0.5, 1), mgp = mgp)
    barplot(NND, col = cols_tr[-i], ylim = c(0, 250), las = 2, yaxt = "n", 
            ylab = "", cex.lab = cx)
    axis(2, at=seq(0, 250, 50), cex.axis = cx, las = 2, mgp = mgp, tcl = -0.2)
    mtext("Average distance", side = 2, line = 1.72, cex = 0.4)
    mtext("to neighbour (km)", side = 2, line = 1.2, cex = 0.4)
  })
}
par(xpd = NA)
legx <- grconvertX(0.4, from = "ndc", to = "user")
legy <- grconvertY(0.5, from = "ndc", to = "user")
legend(x = legx, y = legy, legend = "Protected Areas", pch = 15, col = "grey75", 
       bty = "n", pt.cex = 3 * 0.6, cex = 1.5 * 0.6)
dev.off()

@@

### Figures 2 & 3 (probably supplemental)
Deprecated
```{r, eval = FALSE}
# individual maps
# png(full_path(p_figures, "all-4-maps.png"), height = 7, width = 7, 
#      units = "in", res = 300)
# par(mfrow = c(2, 2))#, oma = c(0, 0, 0, 2))
# ftitles <- c("Yield", "Carbon", "Biodiversity", "Cost")
# legp <- c(TRUE, rep(FALSE, 3))
# for(i in 1:4) {
#   dtr <- calc(pure_r[[i]][[1:2]] * c(1, 2), sum)
#   imp_plot2(dtr, impacts = i1, fpath = p_figures, fnm = "all-4-maps", 
#             cexscale = 0.6, ftitle = ftitles[i], crops = c("maize", "soy"), 
#             stats = FALSE, hold = TRUE, legend = legp[i], marg = c(0, 0, 2, 0))
# }
# dev.off()

@@

# select out impacts corresponding to those runs
cstats <- selected_impacts(pind, fp(p_out, ybdc$both$bcode))
cstats <- cstats[, .(iter, conv_area, tot_C, tot_cost, cons_tot)]
# colSums(outtab[1:2, c("conv_area", "tot_C", "tot_cost", "cons_tot")])
# pare[ind %in% pind]

@@

# percent of total possible savings by the 15\% weight to both C and BD
((minmaxstats[2, .(conv_area, tot_C, cons_tot, tot_cost)]) - 
  (imp_pct[4, .(conv_area, tot_C, cons_tot, tot_cost)])) /
  imp_range[, .(conv_area, tot_C, cons_tot, tot_cost)]

cols_tr <- c(rgb(1, 0, 0), rgb(0, 0, 1), rgb(0, 0.75, 1), rgb(1, 0.75, 0))
# sctab <- do.call(rbind, scens) * 100
cx <- 0.7
# lcols <- c("black", "red", "blue")
# imp_pct[, {
#   png(fp(p_figures, "weight_impact.png"), height = 4, width = 4, 
#       units = "in", res = 300)
#   par(mgp = c(2, 0.75, 0), mar = c(3, 3, 1, 1))
#   plot(conv_area, tot_C, type = "l", xlab = "", ylab = "", #xaxt = "n", 
#   lines(conv_area, int_prior, col = "red")
#   lines(conv_area, mu_cost, col = "blue")
#   axis(1, at = seq(2, 12, 1), cex = cx, cex.axis = cx, line = -0.25, 
#        tcl = -0.2, mgp = c(1, 0.25, 0))
#   axis(2, at = seq(0, 60, 5), las = 2, cex = cx, cex.axis = cx, line = -0.25, 
#        tcl = -0.15, mgp = c(1, 0.25, 0))
#   mtext("% land savings", side = 1, line = 1, cex = cx)
#   mtext("% Carbon/Biodiv/Cost savings", side = 2, line = 1, cex = cx)
#   inms <- c("tot_C", "int_prior", "mu_cost")
#   for(i in 1:length(inms)) {
#     text(conv_area[-1], get(inms[i])[-1], labels = sctab[-1, i + 1], 
#          cex = cx * 0.8, pos = 3, offset = 0.2, col = lcols[i])
#     text(conv_area[1] + 0.1, i, labels = 0, cex = cx * 0.8, pos = 3, 
#          offset = i * 0.15 - 0.2, col = lcols[i])
#   }
#   legend("bottomleft", legend = c("Carbon", "Biodiv", "Cost"), cex = cx,
#          text.col = lcols, col = lcols, bty = "n", lty = 1)
imp_pct[, {
  png(fp(p_figures, "weight_impact5.png"), height = 4, width = 4, 
      units = "in", res = 300)
  plot(xwgts, conv_areap, type = "l", xlab = "", ylab = "", axes = FALSE, 
       ylim = c(0, 55), col = cols_tr[1])
  lines(xwgts, tot_Cp, col = cols_tr[2])
  lines(xwgts, cons_totp, col = cols_tr[3])
  lines(xwgts, tot_costp, col = cols_tr[4])
  axis(1, at = xwgts, labels = seq(0, 90, 10), cex = cx, cex.axis = cx, 
       line = -0.25, tcl = -0.2, mgp = c(1, 0.25, 0))
  axis(2, at = seq(0, 55, 5), las = 2, cex = cx, cex.axis = cx, line = -0.25, 
       tcl = -0.15, mgp = c(1, 0.25, 0))
  mtext("% Weight taken from Yield and divided", side = 1, line = 1, cex = cx)
  mtext("equally between Carbon & Biodiversity", side = 1, line = 1.75, 
        cex = cx)
  mtext("% Avoided Cost", side = 2, line = 1, cex = cx)
  legend("bottomright", 
         legend = c("Yield", "Carbon", "Biodiversity", "Travel cost"), 
         cex = cx, text.col = cols_tr, col = cols_tr, bty = "n", lty = 1, 
         inset = c(0, 0.25, 0, 0))
  dev.off()
}]

@@

minmaxstats[1, ] / 10000 * 1.05 - minmaxstats[1, ] / 10000

# indices of costs in other three variables
cost2 <- seq(1, 6, 0.05)
y_comp <- compromise(pare, optirange, cvar = "Y", cost1 = 1.05, cost2 = cost2)
c_comp <- compromise(pare, optirange, cvar = "C", cost1 = 1.05, cost2 = cost2)
bd_comp <- compromise(pare, optirange, cvar = "BD", cost1 = 1.05, cost2 = cost2)
ct_comp <- compromise(pare, optirange, cvar = "COST", cost1 = 1.05, cost2=cost2)
# pare[ind == y_comp["ind"], .(Y, C, BD, COST)] / optirange[1, ]
# pare[ind == c_comp["ind"], .(Y, C, BD, COST)] / optirange[1, ]
# pare[ind == bd_comp["ind"], .(Y, C, BD, COST)] / optirange[1, ]
# pare[ind == ct_comp["ind"], .(Y, C, BD, COST)] / optirange[1, ]

@@

# pull out the impact tables (brief check shows they are the same values)
all_stats <- selected_impacts(unname(pind), fp(p_out, ybdc$both$bcode))
# impsr <- lapply(c(2, 5, 3, 7:9, 4), function(x) all_stats[[x]])
impsr <- lapply(c(2, 3, 5, 4), function(x) all_stats[[x]])

@@

maxes <- sapply(c(2:3, 5, 4), function(j) minmaxstats[[j]][2])
mins <- sapply(c(2:3, 5, 4), function(j) minmaxstats[[j]][1])
ymaxes <- maxes / yscale
ymins <- mins / yscale
pctlines <- rbind(ymins, 
                  t(sapply(c(0.25, 0.5, 0.75), function(x) {
                    (ymaxes - ymins) * x + ymins
                  })), ymaxes)

@@

ftits <- list("Compromise 5% on Yield", "Compromise 5% on Carbon", 
              "Compromise 5% on Biodiversity", "Compromise 5% on Travel Cost")
yaxes <- list(seq(0, 16, 4), seq(0, 1200, 100), seq(0, 9, 1), 
              seq(0, 35, 5))
pcttxt <- c("best", "50%", "worst")
impsr

# plot
png(fp(p_figures, "compromise_5pct3.png"), height = 3.5, 
    width = 7, units = "in", res = 300)
l <- layout(mat = lmat)
# layout.show(l)

# map plots
legtf <- c(FALSE, FALSE, FALSE, FALSE)
for(i in 1:4) { # i <- 1
  # plot(zambia)
  imp_plot2(toresr[[i]], impacts = i1, fpath = p_figures, fnm = "bob",
            crops = "", ftitle = ftits[[i]], col = cols_tr[[i]], 
            legend = legtf[i], hold = TRUE, stats = FALSE, cexscale = 0.4, 
            marg = rep(0, 4))
}  
# impact plots
mgp <- c(0.8, 0.25, 0)
cx <- 0.6
for(i in 1:4) { 
  v <- impsr[[i]][1:4] / yscale[i]
  par(mar = c(2, 3.5, 2, 0))
  b <- barplot(v, las = 2, col = cols_tr, mgp = c(1, 0.25, 0), tcl = -0.2, 
               yaxt = "n", ylim = range(yaxes[[i]]), ylab = ylabs[i], 
               cex.axis = cx, cex.lab = 0.7)
  for(j in 1:3) {
    lines(c(-1, 7), rep(pctlines[j + (j - 1), i], 2), lwd = 1, col = "grey50")
    text(4.5, y = rep(pctlines[j + (j - 1), i], 2), labels = pcttxt[j], 
         col = "grey50", xpd = NA, pos = 4, cex = cx * 0.9)
  }
  axis(2, at = yaxes[[i]], cex.axis = cx, las = 2, mgp = mgp, tcl = -0.2)
  ind <- which(pms2bb[, paste0("Var", i)] == 1)
  with(pms2bb[ind, ], {
    par(mar = c(0.5, 3, 2, 1), mgp = mgp)
    barplot(JS, col = cols_tr[-i], ylim = c(0, 70), yaxt = "n", 
            ylab = "% Overlap", cex.lab = cx)
    axis(2, at=seq(0, 70, 10), cex.axis = cx, las = 2, mgp = mgp, tcl = -0.2)
    par(mar = c(2, 3, 0.5, 1), mgp = mgp)
    barplot(NND, col = cols_tr[-i], ylim = c(0, 30), las = 2, yaxt = "n", 
            ylab = "", cex.lab = cx)
    axis(2, at=seq(0, 30, 10), cex.axis = cx, las = 2, mgp = mgp, tcl = -0.2)
    mtext("Average distance", side = 2, line = 1.3, cex = 0.4)
    mtext("to neighbour (km)", side = 2, line = 0.8, cex = 0.4)
  })
}
par(xpd = NA)
legx <- grconvertX(0.4, from = "ndc", to = "user")
legy <- grconvertY(0.5, from = "ndc", to = "user")
legend(x = legx, y = legy, legend = "Protected Areas", pch = 15, col = "grey75",        bty = "n", pt.cex = 3 * 0.6, cex = 1.5 * 0.6)
dev.off()

@@

png(fp(p_figures, "compromise_25pct2.png"), height = 2, width = 4, 
    units = "in", res = 300)
l <- layout(mat = lmat)
# layout.show(l)

@@

for(i in 1:4) {
  1 - print(all_stats[5, c(2:3, 5, 4), with = FALSE] / 
              all_stats[i, c(2:3, 5, 4), with = FALSE])
}

# equal compromise avoided cost
for(i in 1:5) {
  print(((minmaxstats[2, c(2:3, 5, 4), with = FALSE]) - 
     (all_stats[i, c(2:3, 5, 4), with = FALSE])) /
    imp_range[, c(2:3, 5, 4), with = FALSE])
}

# equal cost difference relative to best case
for(i in 1:5) {
  print(((all_stats[i, c(2:3, 5, 4), with = FALSE]) - 
     (minmaxstats[1, c(2:3, 5, 4), with = FALSE])) /
    imp_range[, c(2:3, 5, 4), with = FALSE])
}

@@

ftits <- c("Maximize Yields", "Compromise Equally")
leg <- c("converted", "farmblock", "converted in farmblock")
inlist <- list("Y" = yfbr, "eqwt" = eqfbr)
png(fp(p_figures, "fb_overlaps.png"), height = 2.5, width = 5, units = "in", 
     res = 300)
par(mfrow = c(1, 2))
for(i in 1:2) {
  imp_plot2(inlist[[i]], impacts = i1, fpath = p_figures, fnm = "bob",
            crops = leg, ftitle = ftits[i], 
            col = c("red", "orange", rgb(0, 1, 1)),
            legend = TRUE, hold = TRUE, stats = FALSE, cexscale = 0.3, 
            marg = c(0, 0, 1, 0), inset = c(0, 0, 0, 0), titline = 0)
  mtext(paste("% Overlap =", round(fb_sim[i], 2)), side = 3, line = -2, 
        cex = 0.4, adj = 0.2)
  mtext(paste("Mean dist. to neighbour =", round(fb_nnd[i]), "km"), side = 3,
        line = -2.5, cex = 0.4, adj = 0.2)
}
dev.off()

@@

lowi <- selected_impacts2(lowgap$impacts)
highi <- selected_impacts2(highgap$impacts)
gaptab <- rbind(lowi, all_stats[5, names(all_stats)[-1], with = FALSE], highi)
gaptab[1, ] / gaptab[2, ] - 1
gaptab[3, ] / gaptab[2, ] - 1
gaptab[, tot_C / 100000]

@@

### Additional supplementals
```{r, eval = FALSE}
il <- mzsoyto$inputs
ylds <- dt_to_raster(cbind(basedt[, .(x, y)], il$p_yield), CRSobj)
carb <- dt_to_raster(cbind(basedt[, .(x, y)], il$carbon), CRSobj)
cost <- dt_to_raster(cbind(basedt[, .(x, y)], il$cost), CRSobj)
bd <- dt_to_raster(cbind(basedt[, .(x, y)], il$cons), CRSobj)
closs <- carb[[1]] + carb[[2]] * 0.25
pacols <- c("transparent", "grey85", "grey75")
